Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-08-21 submission/manuscript.Rmd
update methods

## Whole genome bisulfite sequencing (WGBS)
Genomic DNA (gDNA) from na&#239;ve ESCs and extended EpiLCs was extracted using the Wizard Genomic DNA Purification Kit (Promega A1120), following the instructions for Tissue Culture Cells. gDNA was sent to Novogene for WGBS using the Illumina NovaSeq X Plus platform and sequenced for 150bp paired-end reads (PE150).

>>>>

## Whole genome bisulfite sequencing (WGBS)
Genomic DNA (gDNA) from na&#239;ve ESCs and extended EpiLCs was extracted using the Wizard Genomic DNA Purification Kit (Promega A1120), following the instructions for Tissue Culture Cells. gDNA from two wild-types and two _Kdm5c_-KOs of each cell type was sent to Novogene for WGBS using the Illumina NovaSeq X Plus platform and sequenced for 150bp paired-end reads (PE150). 
- bismark
- Methylkit
